The error in Bayesian phylogenetic reconstruction when speciation is not instantaneous

### 2018-09-17 article.tex
Changes of @rsetienne

\richel{Start new}
The PBD model has five parameters, depicted in table \ref{table:parameters}. 
The speciation completion rates $\lambda$ we use are $0.1$, $0.3$, $1.0$ and $10^9$ probability of occurence per time unit. 
\richel{Is the unit correct unit now?}
The extinction rates $\mu = \mu_g = \mu_i$ we use are $0.0$, $0.1$ and $0.2$ probability of occurence per time unit.
We use expected mean tree sizes $n$ of 50, 100 and 200 good taxa.
From each combination of $\lambda$, $\mu$ and $n$, we derive a speciation initiation rate $b = b_i = b_g$, shown in table \ref{table:pbd_parameters}.
Our parameters are inspired on existing work \cite{etienne_and_rosindell_2012}\cite{etienne2014}.
We use $\lambda = 10^9 \approx \infty$ to let the PBD model reduce to the BD model.

@@

This research creates two data sets: a general one, to explore parameter space, 
and one to investigate the effect of sampling incipient species (see below).
For the general data set, all the trees with the correct number of good species are kept.
For the data set to investigate sampling, only trees with the additional constraint of sampling having an effect are kept.
As sampling does not have an effect for $\lambda = \infty$, this parameter value is absent in that data set.
\richel{End new}

@@

We compare each posterior phylogeny to the (sampled) species tree
using the nLTT statistic (\cite{janzen2015}), from the \verb;nLTT; package (\cite{nltt}). 
The nLTT statistic equals the area between the normalized
lineages-through-time-plots of two phylogenies, which has a range 
from zero (for identical phylogenies) to one. We use inference error 
and nLTT statistic interchangeably. Comparing the simulated species tree
with each of the posterior species trees yields a distribution of nLTT statistics. 
\richel{Start new}
The input trees generated with a $\lambda = 10^9$ allow us to measure the noise of the experiment.
For $\lambda = \infty$, the PBD model that generates the starting trees reduces to a BD model.
In the following steps, sampling will have no effect, BEAST2 will assume the correct speciation model,
and the difference between inferred tree and true species tree are explained purely due to this experimental noise.
\richel{End new}

>>>>

\richel{Start new}
The PBD model has five parameters, depicted in table \ref{table:parameters}. 
The per species speciation completion rates $\lambda$ we use are $0.1$, $0.3$, $1.0$ and $10^9$. This means that there is a $0.15 dt$ ($0.35 dt$, $1.0 dt$, $10^9 dt$) probability of speciation completion occurring in an infinitesimal time $dt$. 
We use per species extinction rates of $\mu = \mu_g = \mu_i$ $0.0$, $0.1$ and $0.2$.
For each combination of $\lambda$, $\mu$ and $n$, we use a speciation initiation rate $b = b_i = b_g$ that gives a given value of the expected number of species. We use expected mean tree sizes $n$ of 50, 100 and 200 good taxa and the corresponding speciation initiation rates for all parameter combinations are shown in table \ref{table:pbd_parameters}.
Our parameters are inspired by existing work on protracted speciation \cite{etienne_and_rosindell_2012}\cite{etienne2014}.
We use $\lambda = 10^9 \approx \infty$ as our control for which the PBD model reduces to the BD model.

@@

We create two data sets: a general one, to explore parameter space, 
and one to investigate the effect of sampling incipient species (see below).
For the general data set, all the trees with the correct number of good species are kept.
For the data set to investigate sampling, only trees with the additional constraint of sampling having an effect are kept.
As sampling does not have an effect for $\lambda = \infty$, this parameter value is absent in that data set.
\richel{End new}

@@

We compare each posterior phylogeny to the (sampled) species tree
using the nLTT statistic (\cite{janzen2015}), from the \verb;nLTT; package (\cite{nltt}). 
The nLTT statistic equals the area between the normalized
lineages-through-time-plots of two phylogenies, which has a range 
from zero (for identical phylogenies) to one. We use inference error 
and nLTT statistic interchangeably. Comparing the simulated species tree
with each of the posterior species trees yields a distribution of nLTT statistics. 
\richel{Start new}
The input trees generated with a $\lambda = 10^9$ allow us to measure the noise of the experiment.
For $\lambda = \infty$, the PBD model that generates the starting trees reduces to a BD model.
In the subsequent steps, sampling will have no effect in this case, because BEAST2 will assume the correct speciation model,
so the difference between inferred tree and true species tree are explained purely due to this experimental noise.
\richel{End new}
